Probabilistic Topic Modelling to Reduce the Noise in Metabolomics

### 2016-12-06 docs/MSci_proposal/mprop.tex
First two paragraphs review.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Probabilistic Topic Modelling for Reducing the Impact of Noise in Metabolomics}
\author{Arijus Pleska}
\date{Date of submission placed here}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Metabolomics
% Vision

\section{Introduction}

% Intro
% - ML in biology
% - Data patterns
% - Noise
\par This research proposal suggests an application of machine learning in biology. We intend to study the scans of low level biological entities in order to derive their patterns. To be more specific, we aim to tackle the issue of noise, which arises from the hardware limitation of the data collection devices.

% Metabolomics
% - Definition
% - Data gatheting technology
\par The branch of biology we are expecting to carry out the research is metabolomics. In brief, metabolomics is the scientific study of chemical processes which involve small molecules -- metamobilites. These chemical processes can be predicted by the features of metabolites; and metabolites are these low level biological entities. By using mass spectrometers, we can obtain the masses and intensities of metabolites. Note that the mass suggests different types of metabolites, whereas the intensity displays the level of concentration. Thereby, a mass spectrum can be used to distinguish and visualise the observed metabolites; and combinations of specific metabolites types   may suggest a specific pattern for the chemical process leading to a particular formation.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Probabilistic Topic Modelling to Reduce the Noise in Metabolomics}
\author{Arijus Pleska}
\date{Date of submission placed here}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Metabolomics
% Vision
\section{Introduction}

% Intro
% - ML in biology
% - Data patterns
% - Noise
\par This research proposal suggests an application of machine learning in biology. We intend to study the scans of low level biological entities in order to derive their patterns. To be more specific, we will be tackling a problem of noise. This issue of noisiness arise from the hardware limitation of the high precision data collection devices.

% Metabolomics
% - Definition
% - Data gatheting technology
\par The branch of biology we are expecting to carry out the research is metabolomics. In brief, metabolomics is the scientific study of chemical processes which involve small molecules -- metamobilites. Note that these chemical processes can be predicted by the features of metabolites. More specifically, mass spectrometry (MS) is often used to gather metabolite data sets. By this technique, we have information on the masses and intensities of the metabolites within a sample, i.e., we have the mass spectrum of a sample. Note that a different mass suggests different types of metabolites, whereas intensity suggests the level of concentration. Thereby, a mass spectrum is used to distinguish and visualise the observed metabolites. By deriving the formulae of specific metabolites types, we can induce patterns leading to the prediction of chemical processes.
